A thesis draft

### 2018-10-10 draft.tex
Add bullet points

We performed an accured analysis of the tools choosen based on their maturity, 
on the community and on the technical support offered (e.g. user manuals, 
developer documentation), which, at the end, commited us to choose different 
tools from the suggested ones. A detailed description of the architectural 
implementation can be found in chapter~\ref{chap:archimpl}.

>>>>

We performed an accured analysis of the tools choosen based on their maturity, 
on the community and on the technical support offered (e.g. user manuals, 
developer documentation), which, at the end, commited us to choose different 
tools from the suggested ones. A detailed description of the architectural 
implementation can be found in chapter~\ref{chap:archimpl}.\todo{Include prof. 
survey about community components here}

\item VNFs this are the core components that perform packets manipulation 
\todo{Expand}

\item NFV Management and Orchestration (MANO) \todo{Expand this part}
